\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-22 paper.tex
3.1

\subsection{Abstraction of bandwidth availability}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer demanding Inter-DC WAN bandwidth resourses could be any application or tenant  spanning multiple DCs, in either a public or a private cloud. 
%a tenant of a public cloud (e.g., Amazon AWS), who uses this substrate to build his own virtual private cloud over multiple DCs, or could be a service team who launches multiple VM instances in a private cloud (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
%Currently, there is no interface for tenants to specify bandwidth availability.
Our abstraction of network failure scenarios and bandwidth availability demands in $\mathsf{BATE}$ are as follows.

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The Inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the DCs, 
and the set of links $V$ represent directed links between them. 
A network scenario $\mathbf{z}=\{mathbf{z}_1,mathbf{z}_2,...,mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($mathbf{z}_i=1$) or down ($mathbf{z}_i=0$), 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
and we also assume network operators can use historical data to estimate the failure probability $x_i$ for this link. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
Then, the expected probability that network scenario  $\mathbf{z}$ will happen \cite{Teavar} is given by 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i)(x_i))
\end{eqnarray}

\textbf{To be updated, follow Fig.1 )
For example, an inter-DC WAN contains three links $E=\{e_1,e_2,e_3\}$. 
Network scenario $\{1,1,0\}$ means $e_1$ ,$e_2$ are available and  $e_3$ fails.
If the up probability of $e_1,e_2,e_3$ are 0.9, 0.8, 0.85, respectively.
Then its probability $p(\{1,1,0\}) =0.9\times0.8\times0.15=0.108$.

@@

\textbf{Traffic engineering model:}
Our Traffic Engineering uses tunnel-based forwarding \cite{FFC,swan,Teavar}.%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
We use $D$ and $\hat{D}$ to represent arrived demands and \textit{admitted} demands, respectively.
Given a demand $d$, our traffic engineering scheme will decide whether to admit it (i.e., $g_d$), 
and the bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ over tunnel $t$ will be $f_d^t$.
Under the above network failure scenario model, we also use 
$v_t^{\mathbf{z}}$ to denote whether tunnel $t$ is available (i.e., $v_t^{\mathbf{z}}=1$)  or not  (i.e., $v_t^{\mathbf{z}}=0$) under the network scenario $\mathbf{z}$. 
Given an allocation result ${f_d^t | \foreach t \in T_k, k \in K}$, 
if (1) the total bandwidth allocated for each s-d pair $k$, i.e., $\sum_{\foreach t \in T_k} f_d^t}$, 
is equal to the bandwidth demand $\mathbf{b}_d^k$ for that pair, and 
(2) for every tunnel $t$ that is used in the allocation (i.e., $\f_d^t>0$), 
its expected availability under all possible network failure scenarios, 
i.e., $\sum_{\mathbf{z}} \in Z} p_{\mathbf{z}} \times v_t^{\mathbf{z}} $, 
is no less than the availability demand $\beta_d$, 
then we say this BA demand is satisfied by this exact allocation result in a sensen of expectation. 
If a failure indeed occurs, our traffic engineering scheme will try to reroute traffic that is affected by this failure. If any availability target is violated, a refund will be given back to the customer (see $\S$\ref{background}), and we use $h_d$ to denote the profit (after refunding) for demand $d$.

@@

\subsection {Admission control} \label{admission_control}
User demands are served in a first-come-first-service (FCFS) manner without preemption.
When a new demand $d$ arrives, we have $D= $\hat{D}$ \cup {d}$.
%The Admission control  \textit{determines whether availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model}.
%If this is true, the new arrival demand can be admitted, otherwise, it is rejected.
To accommodate as many demands as possible, the optimal admission strategy would be that, 
if every demand in $D$ can meet its availability target, then $d$ should be admitted. 
Otherwise, it should be rejected.
This can be modeled by a 0-1 Mixed-Integer Linear Programming (MILP) problem which  
maximizes the number of demands whose availability targets can be satisfied.
Appendix \ref{admission_problem} shows the formulation of this problem, 
which can be proved to be NP-hard by reducing the all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of it.
%The details are omitted for brevity.
%If availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model, the new arrival demand can be admitted, otherwise, it is rejected.
%If , we can model the 
%The Admission control part decides whether a new demand submitted by a tenant can be admitted or not.

@@

\begin{proof}
The failure recovery problem contains the all-or-nothing multi-commodity flow problem as a special case, which is known as an NP-hard problem\cite{inproceedings2}.
Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
where each pair $s_it_i$ corresponds to a commodity flow to be sent from the source node $s_i$ to the destination node $t_i$ with demand $d_i$.
Let $\mathcal{P}_i$ denote the path set for pair $s_it_i$.
The  all-or-nothing multi-commodity flow problem tries to find a maximum weight routable set:
\begin{equation}
\begin{aligned} \label{P}
&maximize  \sum_{i=1}^k w_i \times y_i\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. &\forall e \in E: \sum_{i=1}^k\sum_{p\in \mathcal{P}_i}f_{ip}L_{pe} \le c_e \\
     &\forall  1\le i \le k  : y_i=
\begin{cases}
1 &\text{$\sum_{p \in \mathcal{P}_i}f_{pt} \ge d_i$}\\
0 &\text{$\sum_{p\in \mathcal{P}_i}f_{pt} < d_i$}
\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
Where $g_i$ denotes whether commodity flow $i$ can be routable.
We transyorm the all-or-nothing multi-commodity flow problem to a special instance of
failure recovery problem and consider a special case, in which $\mu_i=0,\forall d \in \hat{D}$.
In this case, if allocated bandwidth is larger than the demand, then the profit is 1, otherwise, it is 0.
We consider setting the admitted demand from tenants and their bandwidth target in 
the failure recovery as the multi-commodities and their bandwidth demand in the all-or-nothing multi-commodity flow problem.
If we can solve the special case of the admission control problem with a polynomial time algorithm, we would obtain the routable multi-commodity flow set  in the all-or-nothing multi-commodity flow problem.  
Therefore, the failure recovery problem  is at least as hard as the all-or-nothing multi-commodity flow
problem, which is known to be NP-hard. This completes the
proof.
%If we regard $j \in J$ as a multi-commodity flow pair and the topology as the undirected graph.
%$g_j$ denotes whether multi-commodity flow $j$ is able to be routed.
%Then WAPM-S problem can be seen as a variant of all-or-nothing multi-commodity flow problem and it is NP-hardness.
\end{proof}

>>>>

\subsection{Abstraction of bandwidth availability}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer demanding inter-DC WAN bandwidth resources could be any application or tenant  spanning multiple data centers, in either a public or a private cloud. 
%a tenant of a public cloud (e.g., Amazon AWS), who uses this substrate to build his own virtual private cloud over multiple DCs, or could be a service team who launches multiple VM instances in a private cloud (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
%Currently, there is no interface for tenants to specify bandwidth availability.
Our abstraction of network failure scenarios and bandwidth availability demands in $\mathsf{BATE}$ are as follows.

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the data centers, 
and the set of links $V$ represent directed links between them. 
A network scenario $\mathbf{z}=\{\mathbf{z}_1,\mathbf{z}_2,...,\mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $\mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($\mathbf{z}_i=1$) or down ($\mathbf{z}_i=0$), 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
and we also assume network operators can use historical data to estimate the failure probability $x_i$ for this link. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
Then, the expected probability that network scenario  $\mathbf{z}$ will happen \cite{Teavar} is given by 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i)(x_i))
\end{eqnarray}

%\textbf{To be updated, follow Fig.1 }
For example, the inter-DC WAN contains four links $E=\{e_1,e_2,e_3,e_4\} $ shown in Figure \ref{motivatio_fig}. 
Network scenario $\{1,1,0,1\}$ means $e_1$ ,$e_2$, $e_4$ are available and  $e_3$ fails.
The up probability of $e_1,e_2,e_3,e_4$ are 96\%, 99.9999\%, 99.9\%, 99.9999\%, respectively.
Then its probability $p(\{1,1,0,1\}) =0.96\times0.999999\times0.001\times0.999999\simeq 0.000959998$.

@@

\textbf{Traffic engineering model:}
Our Traffic Engineering uses tunnel-based forwarding \cite{FFC,swan,Teavar}.
%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
We use $D$ and $\hat{D}$ to represent arrived demands and \textit{admitted} demands, respectively.
Given a demand $d$, our traffic engineering scheme will decide whether to admit it (i.e., $g_d$), 
and the bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ over tunnel $t$ will be $f_d^t$.
Under the above network failure scenario model, we also use 
$v_t^{\mathbf{z}}$ to denote whether tunnel $t$ is available (i.e., $v_t^{\mathbf{z}}=1$)  or not  (i.e., $v_t^{\mathbf{z}}=0$) under the network scenario $\mathbf{z}$. 
Given an allocation result ${f_d^t}$, 
(i) if the total bandwidth allocated for \textbf{each} s-d pair $k$ through the total surviving tunnels under network scenario $\mathbf{z}$, i.e., $\sum_{\forall t \in T_k} f_d^tv_t^{\mathbf{z}}$, 
is not smaller than demand $\mathbf{b}_d^k$ for that pair under under scenario $\bm{z}$,  then we call the scenario as a qualified one;
(ii) The sum of qualified scenario probability can be seen as the achieved availability and if the achieved availability
%(ii) for every tunnel $t$ that is used in the allocation (i.e., $f_d^t>0$), 
%its expected availability under all possible network failure scenarios, 
%i.e., $\sum_{\mathbf{z}} \in Z p_{\mathbf{z}} \times v_t^{\mathbf{z}} $, 
is no less than the availability demand $\beta_d$, then we say this BA demand is \textbf{satisfied} by this exact allocation result. 
%<<<<<<< HEAD
%then we say this BA demand is \textbf{satisfied} by this exact allocation result. 
%=======
%then we say this BA demand is satisfied by this exact allocation result in a sensen of expectation. 
%>>>>>>> 7d80e71feb4d10a0f1449a95f5e091001064f259
If a failure indeed occurs, our traffic engineering scheme will try to reroute traffic that is affected by this failure. If any availability target is violated, a refund will be given back to the customer (see $\S$\ref{background}), and we use $h_d$ to denote the profit (after refunding) for demand $d$.

@@

\subsection {Admission control} \label{admission_control}
User demands are served in a first-come-first-service (FCFS) manner without preemption.
When a new demand $d$ arrives, we have $D= \hat{D} \cup {d}$.
%The Admission control  \textit{determines whether availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model}.
%If this is true, the new arrival demand can be admitted, otherwise, it is rejected.
To accommodate as many demands as possible, the optimal admission strategy would be that, 
if every demand in $D$ can meet its availability target, then $d$ should be admitted. 
Otherwise, it should be rejected.
This can be modeled by a 0-1 Mixed-Integer Linear Programming (MILP) problem which  
maximizes the number of demands whose availability targets can be satisfied.
Appendix \ref{admission_problem} shows the formulation of this problem, 
which can be proved to be NP-hard by reducing the all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of it.
%The details are omitted for brevity.
%If availability target of $\forall d \in D$ can be supported simultaneously subject to network failure model, the new arrival demand can be admitted, otherwise, it is rejected.
%If , we can model the 
%The Admission control part decides whether a new demand submitted by a tenant can be admitted or not.

@@

\begin{proof}
The failure recovery problem contains the all-or-nothing multi-commodity flow problem as a special case, which is known as an NP-hard problem\cite{inproceedings2}.
Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
where each pair $s_it_i$ corresponds to a commodity flow to be sent from the source node $s_i$ to the destination node $t_i$ with demand $d_i$.
Let $\mathcal{P}_i$ denote the path set for pair $s_it_i$.
The  all-or-nothing multi-commodity flow problem tries to find a maximum weight routable set:
\begin{equation}
\begin{aligned} \label{P}
&maximize  \sum_{i=1}^k w_i \times y_i\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. &\forall e \in E: \sum_{i=1}^k\sum_{p\in \mathcal{P}_i}f_{ip}L_{pe} \le c_e \\
     &\forall  1\le i \le k  : y_i=
\begin{cases}
1 &\text{$\sum_{p \in \mathcal{P}_i}f_{pt} \ge d_i$}\\
0 &\text{$\sum_{p\in \mathcal{P}_i}f_{pt} < d_i$}
\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
Where $y_i$ denotes whether commodity flow $i$ can be routable.
We transform the all-or-nothing multi-commodity flow problem to a special instance of
failure recovery problem and consider a special case, in which $\mu_d=0,\forall d \in \hat{D}$.
In this case, if allocated bandwidth is larger than the demand, then the profit is 1, otherwise, it is 0.
We consider setting the admitted demand from tenants and their bandwidth target in 
the failure recovery as the multi-commodities and their bandwidth demand in the all-or-nothing multi-commodity flow problem.
If we can solve the special case of the admission control problem with a polynomial time algorithm, we would obtain the routable multi-commodity flow set  in the all-or-nothing multi-commodity flow problem.  
Therefore, the failure recovery problem  is at least as hard as the all-or-nothing multi-commodity flow
problem, which is known to be NP-hard. This completes the
proof.
%If we regard $j \in J$ as a multi-commodity flow pair and the topology as the undirected graph.
%$g_j$ denotes whether multi-commodity flow $j$ is able to be routed.
%Then WAPM-S problem can be seen as a variant of all-or-nothing multi-commodity flow problem and it is NP-hardness.
\end{proof}
